The Astropy Project

### 2017-10-04 main.tex
more features

@@

\subsubsection{Enhanced CSV format}

\subsubsection{ASCII, FITS, etc.}

@@

List of key new features:

@@

    \item[ASCII: HTML tables]
		TODO.

	\item [FITS: command-line scripts (fitsheader, fitsinfo)]
		TODO.

	\item [FITS: lazy loading (v1.3)]
		The \package{astropy.io.fits} sub-package now supports \emph{lazy
		loading}, where all HDUs are not loaded until they are requested (or
		the file is closed). This should provide substantial speedups for
		situations using the convenience functions (e.g., \texttt{getheader()}
		or \texttt{getdata()}) to get HDU’s that are near the front of a file
		with many HDU’s.

	\item [Misc: YAML serialization (v1.3)]
		The new \astropy{astropy.io.misc.yaml} module
		allows converting astropy objects into a standard YAML format.

>>>>

\inlinecomment{SCO}{Pyfits deprecation in favor of io.fits ?}
\inlinecomment{SCO}{Table and FITS tables}

@@

@@

@@

    \item[ASCII: HTML tables (v0.4)]

		The \package{astropy.io.ascii} sub-package now provides the capability
		to read a table within an HTML file or web URL into an astropy
		\texttt{Table} object. This requires the \package{BeautifulSoup4}
		package to be installed.  Conversely a \texttt{Table} object can now
		be written out as an HTML table.

	\item [Enhanced CSV format (v1.0)]

		One of the problems when storing a table in an ASCII format is
		preserving table meta-data such as comments, keywords and column data
		types, units, and descriptions. Using the newly defined \emph{Enhanced
		Character Separated Values} (ECSV) format it is now possible to write
		a table to an ASCII-format file and read it back with no loss of
		information. The ECSV format has been designed to be both
		human-readable and compatible with most simple CSV readers.

	\item [FITS: command-line scripts (\texttt{fitsheader}, \texttt{fitsinfo}, v0.4)]

		The \package{astropy.io.fits} sub-package now provides a command line
		script for inspecting the header(s) of a FITS file.  Running
		\texttt{fitsheader file.fits} in a terminal prints the header
		information to the screen in a human-readable format. Run
		\texttt{fitsheader --help} to see the full usage documentation.

	\item [FITS: lazy loading (v1.3)]

		The \package{astropy.io.fits} sub-package now supports \emph{lazy
		loading}, where all HDUs are not loaded until they are requested (or
		the file is closed). This should provide substantial speedups for
		situations using the convenience functions (e.g., \texttt{getheader()}
		or \texttt{getdata()}) to get HDU’s that are near the front of a file
		with many HDU’s.

	\item [Misc: YAML serialization (v1.3)]

		The new \package{astropy.io.misc.yaml} module allows converting
		astropy objects into a standard YAML format.
